---
title: "lab 10"
author: "Eli Schulman"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(usethis)
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```


## Beep + for loop
```{r}
# beep() make a noise depending on the number
beepr::beep(9)

# use for loop + beep
for(i in rev(seq(1:5))) {
  print(paste(i, "bottles of beer on the wall"))
}

# beep() in this case creates a sound after the for loop has completed 
beep(9)
```

## Praise is nice
```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner} well")
```

## Cowsay to have characters say something
```{r}
say("Hello World!", by = "yoda")
```

## run usethis::edit_r_profile() in the console to make changes to RStudio profile

## Create connection to github if you started r.proj as non-version controlled
### Run these sequentially in the console
- usethis::use_git()
- usethis::use_github()
### To rename branch using the code from GitHub, run that in the terminal
git branch -m master main
git fetch origin
git branch -u origin/main main
git remote set-head origin -a

## Paletteer --> aggregated color palettes

- to view all of the color palettes available in paletteer, run view(palettes_d_names) in the console. The length of the palette must be at least as long as the length of the data you are displaying
```{r}
## to view all of the palettes available 
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 6, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("nbapalettes::lakers_alt")
```

## Map of Jornada LTER Vegetation
```{r}

```



